\subsection{Slack} \label{sec:slack}

We have a wide variety of very open channels on LSSTC Slack, these include large numbers of science collaborators and members of the astronomy community.
Prior to October 2024, AuxTel and Simonyi star tracker images were shared frequently on certain Slack channels which are not private.
There is the possibility to have private channels on Slack --- we have a few in LSSTC Slack and tend to avoid them for several reasons: they are not discoverable, some bots don't work in them, etc.
Even using Private channels, we face a problem in LSSTC Slack of members potentially inviting non-staff to the channel where images may be shown.

The LSSTC Slack workspace was intentionally conceived as a community (including LSST Science Collaborations) inclusive space. 
Since September 2024 we have been operating a separate Rubin Observatory Slack workspace, whose access is restricted to ``Rubin team members.''  
This has the following data security and privacy benefits.

\begin{itemize}
\item  All Rubin Slack channels are available to all staff in the space --- no problem sharing images as long as ALL agree they never leave the space.
This allows us a great internal space to enjoy successes as they arise.
\item  Fail quietly: We need a workspace where we can openly discuss problems (e.g. “omg what if we crack the AuxTel array” discussion in an open channel)
\item Embargo: Freely post data without having to stop and think whether it is embargoed.
\item GitOps: Slack is “the UNIX command line” for highly distributed teams. SQuaRE offers (and plans on expanding its offerings) of slackbots that actively manipulate project resources, report on project data, issue alerts on operational services etc. Being assured that only trusted staff have access allows us to expand what these services can do.
\item High Priority:  Rubin Slack gives a high-importance lower volume workspace that we can less disruptively monitor out of hours, during holidays and vacations and overall busy times, reducing the communication attack surface.
\item Privacy: We already pin phone numbers to certain channels, and there are concerns about freely sharing staff phone numbers, vacation schedules etc
\item On/Off-boarding: Even if someone is off-boarded from the project, there are legitimate reasons they should still maintain their wider community slack access. A staff-only slack can be tightly controlled together with other high value observatory access.
\item Slack Culture: We have issues where slack cultures clash, eg. community folks at-channel just because a seminar is about to start, respecting quiet days etc. A separate workspace can maintain a more ops-oriented slack culture. It is also easier to respond to inappropriate behavior when it’s your own staff engaging in it.
\end{itemize}

There are some risks associated with a private Rubin-only Slack:

\begin{itemize}
\item ``We are at risk of abandoning the community'': The motivation behind LSSTC was to establish good working relationships with non-observatory staff, particularly DESC. This was at a time when Slack had very poor support for multiple workspaces and guest channel access. Moreover the LSSTC workspace is now well established for this purpose and ops leaders will remain reachable on it.
\item  ``It's fine, we have private channels'': The proliferation of private channels in slack can be a bit of a nightmare. It leads to staff always wondering who should or should not have access to them, and are liable to forget to add new people, forget to off-board departing people, be unclear what channels  should or should not be private, etc. It also leads to reduced transparency within the project --- a number of channels that were open in the original Rubin slack space were made private when we moved to the LSSTC slack.
\item  ``Too hard to determine who is staff'': It's true that the proliferation of in-kind, grad students and other participants have muddied the waters. However this is a problem we still have in the current set-up -  it's just less obvious. The most clear heuristics include “are we paying (corollary: can we “fire”) someone who has violated project rules; are they on the builder's accrual list; do they have summit access; etc.
\item  ``We already say we don't do community user support on Slack'': This is true, we do say it, but we should recognize that it's emotionally hard work when someone is asking a question on Slack to determine whether they are staff or no, and if not to tell them to go elsewhere. Sometimes we just answer without checking, which muddies our stance.
\item  ``We're too busy for this kind of change'': True, but this will only get worse. There is also a plan being prepared to provide more consistent naming for certain types of channels (support, status, etc.) and update default status semantics,  so this would be a good time to implement that.
\end{itemize}


Much as we dislike having ANOTHER Slack space, resurrecting the old LSST Slack space and adding only the team members with image access to it, and then using it for all the the nighttime summit channels has been found to be a clean solution.

\subsubsection{Approach}
See also \secref{sec:genpol}.
Resurrect lsst.slack.com Slack workspace as Rubin Observatory Slack, for restricted use of the Rubin team, at least during commissioning.

Reuse of lsst.slack.com has had some advantages:

\begin{itemize}
\item  It was already set up grandfathered as free so we don't risk applying and being turned down for another free workspace
\item  We can deliberately blur construction / commissioning / ops lines since it is free
\item  Rubin is in total control of configuration, access and any paid features
\item  Workspace was already configured for our use which would speed up any transition

\end{itemize}
We can revisit this approach after commissioning.

Even though this is a private space it is not encrypted and not all project members have access to commissioning data.
Some care, such as not posting full images and certainly not frequently doing so, should be taken.
The assumption is small screen grabs (PNG or JPG)  of features would be shared in this space which is fine.
